Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
update

\begin{frame}{Section 9: Extended Source Search}
  \begin{itemize}
    \item Run a dedicated search 
    \item Try to find previously-unresolved
      extended 2FGL sources
    \item Search for $E>1$ GeV and $E>10$ GeV
    \item Many difficulties in search, discussed at length in text\dots
    \item Publish only good candidates
  \end{itemize}
\end{frame}

\begin{frame}{Fig. 12: Systematics in the plane}
  \includegraphics[scale=0.5]{plots/example_bad_fit_color.pdf}
\end{frame}

>>>>

\begin{frame}{Section 9: Extended Source Search}
  \begin{itemize}
    \item Run a dedicated search for new
    extended 2FGL sources
    \item Test for extension using pointlike, crosscheck with gtlike
    \item Search for $E>1$ GeV and $E>10$ GeV
    \item Many difficulties in search, discussed at length in text\dots
    \item Publish only good candidates
  \end{itemize}
\end{frame}

\begin{frame}{Fig. 12: Systematics in the plane}
  \begin{columns}
    \column{.60\textwidth} 
  \includegraphics[scale=0.5]{plots/example_bad_fit_color.pdf}
    \column{.40\textwidth} 
    \begin{itemize}
    \item Easy to find ``Significantly'' extended sources
    in the galactic plane
    \item Caused by residuals due to
    \begin{itemize}
    \item Diffuse residuals
    \item Unmodeled or incorrectly modeled sources
    \end{itemize}
    \item No easy solution, in the text we discared these sources
      \end{itemize}
  \end{columns}
\end{frame}
